The Astropy Project

### 2017-12-11 main.tex
add "cite" column to provisional

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
In this figure, the color of the cell indicates the maximum difference (in
arcsec) between the two tools over the 1000 longitude-latitude pairs tested.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the maximum difference between longitude-latitude
    values in a set of 1000 random points transformed from FK4 to Galactic
    with the different packages.
    Darker colors (larger differences) are more significant disagreements.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

@@

The \package{astropy.convolution} subpackage implements
``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
reconstruction technique, in which missing data are ignored during the
convolution and replaced with values interpolated using the kernel;
An example of this is given in \figurename~\ref{fig:convolution-example}.
In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
convolution approaches were inconsistent, with the latter implementing
normalized convolution, while the former a different approach.
As of version 2.0, the two methods now agree and include a suite of
consistency checks.

@@

\begin{deluxetable*}{cccc}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}

>>>>

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values of the FK4 to Galactic
    transformation between the different packages. Each comparison block shows
    four squares representing the median, mean, maximum and standard deviation
    going from left to right and bottom to top.
    Darker colors (larger differences) are more significant disagreements.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

@@

The \package{astropy.convolution} subpackage implements
\textit{normalized convolution} \citep[e.g.,][]{Knutsson1993}, an image
reconstruction technique in which missing data are ignored during the
convolution and replaced with values interpolated using the kernel.
An example is given in \figurename~\ref{fig:convolution-example}.
In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
convolution approaches were inconsistent, with only the latter implementing
normalized convolution.
As of version 2.0, the two methods now agree and include a suite of
consistency checks.

@@

\begin{deluxetable*}{cccc}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}
